API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
minor copyedit to grid search example

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel accepts a $\gamma$ parameter,
but actually ignores it. Computing time would thus be wasted, trying out effectively
equivalent settings, if a single hyper-parameter grid was used instead.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

>>>>

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel accepts a $\gamma$ parameter,
but actually ignores it. Computing time would thus be wasted, trying out effectively
equivalent settings, if a single hyper-parameter grid was used instead.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).
